---
title: Quickdraw exploration
subtitle: 
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: false
    theme: cerulean
    toc_float: true
    code_folding: hide
---
  
******
******

```{r setup, include = F}
rm(list=ls())

# load packages
library(tidyverse) 
library(knitr)
library(rmarkdown)
library(broom)
library(langcog)
library(rlist)

FIG_HEIGHT = 4

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F,  cache = F, fig.height = FIG_HEIGHT)
```  

Munge coordinates (mini)
```{r}
m <- jsonlite::stream_in(file("data/json_mini.txt"))

# munge coordinates
m = m %>%
  rowwise() %>%
  do(draw = list.flatten(list(drop(.$drawing)))) %>%
  cbind(m) %>%
  select(-drawing)
```

Munge coordinates
```{r}
d <- jsonlite::stream_in(file("data/bread.ndjson"), 
                        flatten = TRUE)
#save(d, file = "bread")
#load("bread.Rdata")
#dd <- d

# munge coordinates
d %<>%
  rowwise() %>%
  do(draw = list.flatten(list(drop(.$drawing)))) %>%
  cbind(d) %>%
  select(-drawing)
```
```

Drawings by country
```{r}
countries <- read.csv("data/iso_3166_2_countries.csv") %>%
  select(Common.Name, ISO.3166.1.2.Letter.Code)

country.counts = d %>%
  count(countrycode) %>%
  arrange(-n)

country.counts %>%
  filter(n > 1000) %>%
  ggplot(aes(x = countrycode, y = n)) +
  geom_bar(stat = "identity") +
  theme_bw()
  
keep.countries = country.counts = d %>%
  count(countrycode) %>%
  filter(n > 1000)

ds = d %>%
  filter(countrycode %in% keep.countries$countrycode,
         recognized == TRUE) %>%
  select(countrycode, draw) %>%
  inner_join(countries, c("countrycode" = "ISO.3166.1.2.Letter.Code")) %>%
  rename(country = Common.Name) %>%
  filter(!is.na(country))

```

N strokes by country
```{r}
ds %<>% 
  mutate(n_strokes = unlist(lapply(draw, length)),
         mean_length = unlist(lapply(draw, 
                  function(y) mean(unlist(sapply(y, length))))),
         total_time = unlist(lapply(draw, function(y) rev(unlist(y))[1])))
          
strokes.df = ds %>%
  group_by(country) %>%
  multi_boot_standard(column = "n_strokes") 

ggplot(strokes.df, aes(x = reorder(country, mean), y = mean, fill = reorder(country, mean))) +
    geom_bar(position = "dodge", stat = "identity") +
    geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
    theme_bw() +
    ylab("number of strokes") +
    theme(legend.position = "none") +
      theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

```{r}
strokes.length.df = ds %>%
  group_by(country) %>%
  multi_boot_standard(column = "mean_length") 

ggplot(strokes.length.df, aes(x = reorder(country, mean), y = mean, fill = reorder(country, mean))) +
    geom_bar(position = "dodge", stat = "identity") +
    geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
    theme_bw() +
    ylab("mean length of strokes") +
    theme(legend.position = "none") +
      theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

Total time
```{r}
strokes.time.df = ds %>%
  group_by(country) %>%
  multi_boot_standard(column = "total_time") 

ggplot(strokes.time.df, aes(x = reorder(country, mean), y = mean, fill = reorder(country, mean))) +
    geom_bar(position = "dodge", stat = "identity") +
    geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
    theme_bw() +
    ylab("Total Time") +
    theme(legend.position = "none",
    axis.text.x = element_text(angle = 90, hjust = 1)) 
```
First language speakers do longer and fewer strokes. Not a ton of variability in time.

```{r}
ds.coords = ds  %>%
    rowwise() %>%
    do(data.frame(cbind(t(as.data.frame(list.flatten(.$draw))[-3,]),
    as.character(.$country[1]) ))) %>%
    bind_rows() %>%
    rename(x = X1,
           y = X2,
           country = V3)
           
counts = ds.coords %>%
    mutate(x = round(as.numeric(x), 2),
            y = round(as.numeric(y), 2)) %>%
    count(x, y, country)
```

Heat maps
```{r}
ggplot(counts, aes(x, y, colour = n, fill = n)) + 
  facet_wrap(country) +
  geom_tile()

ds.coords %<>%
    mutate(x = as.numeric(x),
           y = as.numeric(y)) 
           
ds.coords %<>% 
    mutate(x.bin = cut_width(x, 100),
           y.bin = cut_width(y, 100))
           
  m = ds.coords %>% 
   filter(country %in% c("Hungary", "Indonesia")) 
    mutate(x.bin = cut_width(x, 100),
           y.bin = cut_width(y, 100))

ds.coords %>%
  filter(country %in% c("Hungary", "Indonesia")) %>%
  ggplot( aes(x = x.bin, y = y.bin)) + 
   facet_wrap("country") +
   geom_point() + 
   stat_density2d(aes(fill=..density..), geom = "tile") +
   scale_fill_gradient2(low = "white", high = "red") +
   #theme_blank() +
   theme(legend.position = "none")
```