---
title: Conceptviz 1 analyses
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: true
    code_folding: hide
---
  
******
******
  
```{r setup, include = F}
rm(list = ls())

# load packages
library(knitr)
library(rmarkdown)
library(langcog)
library(tidyverse)
library(purrr)
library(feather)
library(forcats)
library(googlesheets)
library(jsonlite)
library(broom)
library(corrr)
#source("../R_scripts/helpers.R")

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F, cache = T, fig.height = 4)
```

Measures for 1500 pairs
```{r}
bread_cs <- read_feather("../../../data/keras_similarities/pairwise_country/bread_all_sims.txt") %>%
  select(key_id_1, key_id_2, cosine)

bread_hd_1500 <- read_csv("../../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/bread_sampled_pairs_with_sims_hd.csv", col_types = list( col_character(), col_character(), col_double()))

bread_hd_cs <- left_join(bread_hd_1500, bread_cs) %>%
  mutate(item = "bread")

tree_cs <- read_feather("../../../data/keras_similarities/pairwise_country/tree_all_sims.txt") %>%
  select(key_id_1, key_id_2, cosine)

tree_hd_1500 <- read_csv("../../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/tree_sampled_pairs_with_sims_hd.csv", col_types = list( col_character(), col_character(), col_double()))

tree_hd_cs <- left_join(tree_hd_1500,tree_cs) %>%
  mutate(item = "tree")

all_sims <- bind_rows(bread_hd_cs, tree_hd_cs)

all_sims %>%
  gather("measure", "value", 3:4) %>%
  group_by(measure) %>%
  summarize(mean = mean(value, na.rm = T),
            sd = sd(value, na.rm = T)) %>%
  kable()

cor.test(all_sims$hd_sim, all_sims$cosine)


```

## Read in experimentdata from google sheet
```{r}
d_raw <- gs_title("conceptviz_1_data") %>%
            gs_read()

d <- map_df(d_raw$data, fromJSON, simplifyDataFrame = TRUE) %>%
  bind_cols(subj_id = d_raw$subj_id) %>%
  select(subj_id, everything())
```

## Tidy data
```{r}
d_tidy <- d %>%
  gather(variable, value, -subj_id) %>%
  separate(variable, c("variable", "trial_num"), sep = "_T") %>%
  spread(variable, value) %>%
  mutate_at(c("trial_num", "haus_sim", "rating", "RT", "trial_ID",  "haus_bin"), as.numeric) %>%
  mutate_at(c("category", "drawing_key_id_1", "drawing_key_id_2","trial_type", "subj_id"), as.factor)
```

## Attention Checks
```{r}
d_tidy %>%
  filter(trial_type == "attention_check") %>%
  select(subj_id, rating) %>%
  count(rating) %>%
  ggplot(aes(x = rating, y = n/200)) +
  geom_bar(stat = "identity") +
  ylab("proportion responses")+
  ggtitle("prop. attention checks") +
  theme_minimal()

mean_attention_check_ratings = d_tidy %>%
  filter(trial_type == "attention_check") %>%
  group_by(subj_id) %>% 
  summarize(mean = mean(rating)) %>%
  filter(mean < mean(.$mean))
```

Mostly 1s as correct. 

## hausdorff by decile and ratings
```{r, fig.width = 5}
d_tidy_crit <- d_tidy %>%
  filter(subj_id %in% mean_attention_check_ratings$subj_id) %>%
  filter(trial_type == "critical_trial") 

means_ratings_by_bin <- d_tidy_crit %>%
  group_by(haus_bin, category) %>%
  multi_boot_standard(column = "rating", na.rm = TRUE)

pdf("distance_decile.pdf", width = 5.5, height  = 5)
ggplot(means_ratings_by_bin, aes(x = haus_bin, y = mean, group = category, color = category)) +
  geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper)) +
  geom_smooth(method = "lm") +
  ylab("Mean Similarity Rating") +
  xlab("Hausdorff Distance Decile") +
  ggtitle("Similarity Ratings by Hausdorff Distance Decile") +
       scale_x_continuous(expand = c(0.15, 0), breaks = 1:10) +

  theme(text = element_text(size=13),
      plot.title=element_text(size=14, face = "bold"),
      plot.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      legend.position = "none",
      axis.line = element_line(color = 'black'),
      panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"))  +
    directlabels::geom_dl(aes(label = category), method = list(dl.trans(x = x + .3), "last.bumpup")) 
# https://stackoverflow.com/questions/38088966/directlabels-package-in-r-labels-do-not-fit-in-plot-area
dev.off()
```

## hausdorff continuous and ratings
```{r, fig.width = 5}

d_tidy_crit %>%
  group_by(trial_ID, haus_sim) %>%
  summarize(rating = mean(rating, na.rm = T)) %>%
  ungroup() %>%
  do(tidy(cor.test(.$rating, .$haus_sim))) %>%
  select(-parameter, -method, -alternative) %>%
  kable()
```


There's more variability in hausdorfff distance for bread, relative to tree, which explains the different slopes in the decile plot.

## Hausdorff distance, Modified Hausdorff Distance, and Imagenet-NN cosine
```{r, fig.width = 9}
tree_all_measures <- read_csv(paste0("../../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/balanced_lists/tree_all_measures.csv")) %>%
    mutate_at(c("key_id_1", "key_id_2", "country_code_1","country_code_2"), as.factor) %>%
  select(key_id_1, key_id_2, hd_sim, mhd_sim, cosine, country_code_1, country_code_2) %>%
  mutate(category = "tree")

bread_all_measures <- read_csv(paste0("../../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/balanced_lists/bread_all_measures.csv")) %>%
    mutate_at(c("key_id_1", "key_id_2", "country_code_1","country_code_2"), as.factor)  %>%
  select(key_id_1, key_id_2, hd_sim, mhd_sim, cosine,  country_code_1, country_code_2)  %>%
  mutate(category = "bread")

all_measures <- d_tidy_crit %>%
  rename(key_id_1 = drawing_key_id_1,
         key_id_2 = drawing_key_id_2) %>%
  left_join(bind_rows(tree_all_measures, bread_all_measures), by = c("key_id_1", "key_id_2", "category")) %>%
  select(subj_id, trial_ID, category, rating, haus_sim, cosine, country_code_1, country_code_2, trial_num) %>%
  rename(hd_sim = haus_sim)

all_measures %>%
  gather("measure", "value", 3:5) %>%
  group_by(measure) %>%
  
  do(tidy(cor.test(.$rating, .$value))) %>%
  select(-parameter, -method, -alternative) %>%
  kable()


d_tidy_crit %>%
  group_by(trial_ID, haus_sim) %>%
  summarize(rating = mean(rating, na.rm = T)) %>%
  ungroup() %>%
  do(tidy(cor.test(.$rating, .$haus_sim))) %>%
  select(-parameter, -method, -alternative) %>%
  kable()

all_measures %>%
  group_by(trial_ID, cosine) %>%
  summarize(rating = mean(rating, na.rm = T)) %>%
  ungroup() %>%
  do(tidy(cor.test(.$rating, .$cosine))) %>%
  select(-parameter, -method, -alternative) %>%
  kable()


```

Hausdorff Distance is better than Modified hausdorff Distance (MHD). For bread, MHD > cosine; For tree; MHD = cosine (but there's less variability).

The correlations on the continous measures are modest, but I suspect that's because there's a ceiling on the correlation because we're using a likert scale.

Measure models
```{r}
summary(lmer(rating ~ scale(hd_sim) + scale(cosine) + (1|subj_id), all_measures))
```


Get missing vars
```{r}
## centroids
centroids <- read_tsv("../../../data/supplementary_data/cultural_sim_measures/geo/country_centroids/country_centroids_primary.csv") %>%
  select(ISO3136, LAT, LONG) %>%
  rename(country_code = ISO3136) 

centroids_HK_GE <- centroids %>%
  filter(country_code == "GE") %>%
  bind_rows(data.frame(country_code ="HK", LAT = 22.28552, LONG = 114.15769)) %>%
  bind_rows(centroids)
  
g_centroids <- geosphere::distm(cbind(centroids_HK_GE$LONG, centroids_HK_GE$LAT)) # in meters 
rownames(g_centroids) <- centroids_HK_GE$country_code
colnames(g_centroids) <- centroids_HK_GE$country_code

all_centroid_dists <- reshape2::melt(g_centroids) %>%
  rename(country_code_1 = Var1,
         country_code_2 = Var2,
         centroid_dist_meters = value) 

event_dists <- read_csv("../../../data/supplementary_data/cultural_sim_measures/events/all_google_event_dists.csv")

asjp_dists <- read_csv("../../../data/supplementary_data/cultural_sim_measures/lang/asjp_dists.csv") %>%
  select(-contains("lang"))


all_measures_with_dyadic <- all_measures %>%
  left_join(all_centroid_dists) %>%
  left_join(event_dists) %>%
  left_join(asjp_dists) %>%
  mutate(trial_ID2 = paste0(category, trial_ID))
```

```{r}
item_means <- all_measures_with_dyadic %>%
  mutate(trialname = paste0(category, trial_ID)) %>%
  group_by(trialname) %>%
  summarize(rating = mean(rating)) %>%
  left_join(all_measures_with_dyadic %>% mutate(trialname = paste0(category, trial_ID)) %>% select(-rating), by = "trialname") %>%
  group_by(trialname) %>%
  slice(1) %>%
  select(trialname, rating, category, log_normalized_n_events_all, asjp_dist, centroid_dist_meters) 

item_means %>%
  select(centroid_dist_meters, rating) %>%
    ggplot( aes(x = centroid_dist_meters, y = rating)) +
    geom_point() +
    geom_smooth(method = "lm")


item_means %>%
  select(log_normalized_n_events_all, rating) %>%
    ggplot( aes(x = log_normalized_n_events_all, y = rating)) +
    geom_point() +
    geom_smooth(method = "lm")

item_means %>%
  select(asjp_dist, rating) %>%
    ggplot( aes(x = asjp_dist, y = rating)) +
    geom_point() +
    geom_smooth(method = "lm")


```


```{r}

item_means %>%
  gather("measure", "value", 4:6) %>%
  group_by(measure) %>%
  
  do(tidy(cor.test(.$rating, .$value))) %>%
  select(-parameter, -method, -alternative) %>%
  kable()

########### Here's are the random model: ##################################
summary(lmer(rating ~  scale(centroid_dist_meters) + (1 |trial_ID) + (1|subj_id) + (1|category), all_measures_with_dyadic))

summary(lmer(rating ~  scale(log_normalized_n_events_all) + (1 |trial_ID) + (1|subj_id) +(1|category), all_measures_with_dyadic))

summary(lmer(rating ~  scale(asjp_dist) + (1 |trial_ID) + (1|subj_id) + (1|category), all_measures_with_dyadic))

summary(lmer(rating ~ scale(centroid_dist_meters) + 
               scale(log_normalized_n_events_all) + 
               scale(asjp_dist) +
               (1|trial_ID) + (1|subj_id) + (1|category), 
              all_measures_with_dyadic))

summary(lmer(rating ~  scale(centroid_dist_meters) + category + (1 |subj_id), all_measures_with_dyadic))

summary(lmer(rating ~ scale(centroid_dist_meters) + 
               scale(log_normalized_n_events_all) + 
               category + (1 |subj_id), 
              all_measures_with_dyadic))
#####################################################################
########### Here's are the fixed model: ##################################
summary(lmer(rating ~  scale(centroid_dist_meters) * category + (1|subj_id), all_measures_with_dyadic))

summary(lmer(rating ~ scale(centroid_dist_meters) + 
               scale(log_normalized_n_events_all) + 
               (1|category) + (1|subj_id), 
              all_measures_with_dyadic))

summary(lmer(rating ~  scale(centroid_dist_meters) + category + (1 |subj_id), all_measures_with_dyadic))

summary(lmer(rating ~ scale(centroid_dist_meters) + 
               scale(log_normalized_n_events_all) + 
               category + (1 |subj_id), 
              all_measures_with_dyadic))
#####################################################################


```


Drawing figure
```{r}
bread_stim <- read_csv("../data/sim_experiment_stimuli_bread.csv",  col_types = list(col_integer(), col_character(), col_character(), col_character(), col_double(), col_double()))

SIM_BIN <-10
plot_ids <- bread_stim %>%
  filter(hd_bin == SIM_BIN) %>%
  sample_n(8) %>%
  mutate(id = 1:n()) %>%
  gather("measure", "key_id_num", 3:4) %>%
  arrange(id)

#files <- list.files("../../data/keras_similarities/pair_sim_drawings/images/bread/")
long_files = paste0("../images/drawings/", plot_ids$key_id_num, ".jpeg")

rl = lapply(long_files, image_read)
gl = lapply(rl, grid::rasterGrob)
gridExtra::grid.arrange(grobs = gl, nrow = 8)

# 1 = c("4517415574568960", "5171456952500224")
# 5 = c("5530798088257536", "6476551229014016")
# 10 = c("5507829509128192", "5139027634159616")
```
```