---
title: Compare similarity measures
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: true
    code_folding: hide
---
  
******
******
  
```{r setup, include = F}
rm(list=ls())

# load packages
library(knitr)
library(rmarkdown)
library(langcog)
library(tidyverse)
library(purrr)
library(feather)
library(forcats)
library(magick)
source("../R_scripts/helpers.R")

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F, cache = T, fig.height = 4)
```

Three measures: Cosine similarity, Hausdorff Distance (2 implementations: pracma in R, fast haussdorf module in python), and Modified Hausdorff Distan
ce (in Python).

In quick tests, MHD and HD were correlated ~.7-.96. Neither HD measure was very correlated with cosine, but HD was more correlated. The python implementations are much faster (~4) that R. The "fast" python version was not significantly faster than the not fast MHD in python, but this may not be true at scale.

In conclusion, the best way forward (both computationally fast and accurate), I think is using either HD_fast or MHD on points since points and lines are almost perfectly correlated.

```{r}
ITEM1 <- "tree"
ITEM2 <- "bread"
N_ILE <- 10
GDRAW_SIZE <- 255
IMAGENET_SIZE <- 224
JPEG_SIZE <- IMAGENET_SIZE * 2
N_INTERPOLATE <- 500 # 1000 doesn't look any different (imagenet saw 1000)
JPEG_PATH <- "../../data/keras_similarities/pair_sim_drawings/images/"
```


## Bread
```{r}
raw_data <- read_feather(paste0("../../data/raw_data/feathers/atleast_100/", ITEM2, ".txt"))

img_nums <- c("5759447068573696",
              "6310524302131200", 
              "5439162058539008",
              "5128091204583424",
              "4575892489633792", 
              "5280902294798336",
              "6153535580274688", 
              "6137737331605504")

long_files = paste0("../../data/keras_similarities/pair_sim_drawings/images/bread/", img_nums, ".jpeg")

rl = lapply(long_files, image_read)
gl = lapply(rl, grid::rasterGrob)
gridExtra::grid.arrange(grobs = gl, ncol = 1)

image_read(paste0("../../data/keras_similarities/pair_sim_drawings/images/bread/", img_nums[2], ".jpeg"))

```

Get coordinates
```{r}
raw_combos <- as.data.frame(t(combn(img_nums,2)))

combos <- raw_combos %>%
  rename(key_id_1 = V1, key_id_2 = V2) %>%
  bind_rows(raw_combos %>%
              rename(key_id_2 = V1, 
                     key_id_1 = V2)) %>%
  bind_rows(data.frame(key_id_1 = img_nums, 
                       key_id_2 = img_nums))

```

Neural Nets
```{r}
bread_sims <- read_feather(paste0("../../data/keras_similarities/pairwise_country/", ITEM2 , "_all_sims.txt"))

nn_sims <- combos %>%
          left_join(bread_sims) %>%
          bind_rows(left_join(combos, bread_sims) %>%
                    rename(key_id_1 = key_id_2,
                           key_id_2 = key_id_1)) %>%
  filter(!is.na(cosine)) %>%
  select(-country_code_1, -country_code_2) %>%
  distinct()
```

Hausdorff Distance
```{r}
# https://pdfs.semanticscholar.org/4a04/c3e4d183305aff2e40a6090c366c136fe8f3.pdf

nested_raw <- raw_data %>%
  filter(key_id %in% img_nums) %>%
  mutate(key_id_name = key_id) %>%
  group_by(key_id_name) %>%
  nest() 

long_data = map_df(nested_raw$data, get_image_from_google_draw, 
                                      GDRAW_SIZE,
                                      IMAGENET_SIZE,
                                      N_INTERPOLATE, 
                                      return = "long") %>%
  #bind_rows() %>%
  mutate(key_id = as.factor(key_id))

py2 <- reticulate::py_run_file("../R_scripts/hausdorff_fast_wrapper.py")

system.time(
hd_sims <- map2_df(combos$key_id_1, 
                   combos$key_id_2, 
                   get_hd_distance_fast, 
                   long_data,
                   py2)
)
```

Hausdorff Distance Points only
```{r}
point_data <- raw_data %>%
  filter(key_id %in% img_nums) %>%
  mutate(key_id_name = key_id) %>%
  rename(x_line = x, y_line = y) # this is dumb - it's just teh name in the func

system.time(
pts <- map2_df(combos$key_id_1, 
                   combos$key_id_2, 
                   get_hd_distance_fast, 
                   point_data,
                   py2)
)

 # They're very correlated 
 pts %>%
    rename(hd_sim_pt = hd_sim) %>%
    left_join(hd_sims) %>%
    do(tidy(cor.test(.$hd_sim, .$hd_sim_pt)))
```

Modified Hausdorff Distance
```{r}
py <- reticulate::py_run_file("../R_scripts/mhausdorff.py")
mhd_sims <- map2_df(combos$key_id_1, 
                   combos$key_id_2, 
                   get_mhd_distance, 
                   long_data,
                   py)
```

Plot sims
```{r}
sims <- left_join(hd_sims, nn_sims) %>%
  left_join(mhd_sims) %>%
  mutate(key_id_1 = as.factor(key_id_1),
         key_id_2 = as.factor(key_id_2))

sims$key_id_1 <- fct_recode(sims$key_id_1, 
                          white_bread_1 = "5759447068573696",
                          white_bread_2 = "6310524302131200",
                          white_bread_3 = "5439162058539008",
                          white_bread_4 = "5128091204583424",
                          loaf_1 = "4575892489633792",
                          loaf_2 = "5280902294798336",
                          loaf_3 = "6153535580274688",
                          weird = "6137737331605504")

sims$key_id_2 <- fct_recode(sims$key_id_2, 
                          white_bread_1 = "5759447068573696",
                          white_bread_2 = "6310524302131200",
                          white_bread_3 = "5439162058539008",
                          white_bread_4 = "5128091204583424",
                          loaf_1 = "4575892489633792",
                          loaf_2 = "5280902294798336",
                          loaf_3 = "6153535580274688",
                          weird = "6137737331605504")

sims$key_id_1 <- fct_relevel(sims$key_id_1,c("white_bread_1",
                             "white_bread_2",
                             "white_bread_3",
                             "white_bread_4", 
                             "loaf_1",
                             "loaf_2",
                             "loaf_3",
                             "weird"))

sims$key_id_2 <- fct_relevel(sims$key_id_2,c("white_bread_1",
                             "white_bread_2",
                             "white_bread_3",
                             "white_bread_4", 
                             "loaf_1",
                             "loaf_2",
                             "loaf_3",
                             "weird"))
                        
ggplot(sims, aes(x = key_id_1, y = key_id_2, fill = hd_sim)) +
  geom_tile() +
  theme_bw()

sims %>%
  filter(cosine > .997) %>%
  ggplot(aes(x = key_id_1, y = key_id_2, fill = cosine)) +
  geom_tile() +
  theme_bw()
```

## Tree
```{r, eval = F}

crit_ids <- read_csv(paste0("../../data/keras_similarities/pair_sim_drawings/pair_lists/sampled_", ITEM1 ,"_pairs.csv")) %>%
  #group_by(cosine_bin) %>%
  filter(cosine_bin == 1) %>%
  sample_n(4) %>%
  gather(key_id_name, key_id_num, c(-1:-3, -6:-7)) %>%
  arrange(cosine_bin) %>%
  mutate(key_id_num = as.factor(key_id_num))



long_files = paste0("../../data/keras_similarities/pair_sim_drawings/images/tree/", img_nums, ".jpeg")

rl = lapply(long_files, image_read)
gl = lapply(rl, grid::rasterGrob)
gridExtra::grid.arrange(grobs = gl, ncol = 2)

img_nums <- c("6613114395033600",
              "6557761544388608", 
              "4736045847412736",
              "4688802348007424",
              "5366456621465600", 
              "4707338638327808",
              "4653335464378368", 
              "5142905146572800")
```

```{r}
raw_data <- read_feather(paste0("../../data/raw_data/feathers/atleast_100/", ITEM1, ".txt"))

raw_combos <- as.data.frame(t(combn(img_nums,2)))

combos <- raw_combos %>%
  rename(key_id_1 = V1, key_id_2 = V2) %>%
  bind_rows(raw_combos %>%
              rename(key_id_2 = V1, 
                     key_id_1 = V2)) %>%
  bind_rows(data.frame(key_id_1 = img_nums, 
                       key_id_2 = img_nums))

```


Neural Nets
```{r}
tree_sims <- read_feather(paste0("../../data/keras_similarities/pairwise_country/", ITEM1 , "_all_sims.txt"))

nn_sims <- combos %>%
          left_join(tree_sims) %>%
          bind_rows(left_join(combos, tree_sims) %>%
                    rename(key_id_1 = key_id_2,
                           key_id_2 = key_id_1)) %>%
  filter(!is.na(cosine)) %>%
  select(-country_code_1, -country_code_2) %>%
  distinct()
```

Hausdorff Distance Full
```{r}
nested_raw <- raw_data %>%
  filter(key_id %in% img_nums) %>%
  mutate(key_id_name = key_id) %>%
  group_by(key_id_name) %>%
  nest() 

long_data = map_df(nested_raw$data, get_image_from_google_draw, 
                                      GDRAW_SIZE,
                                      IMAGENET_SIZE,
                                      N_INTERPOLATE, 
                                      return = "long") %>%
  #bind_rows() %>%
  mutate(key_id = as.factor(key_id))


# https://pdfs.semanticscholar.org/4a04/c3e4d183305aff2e40a6090c366c136fe8f3.pdf
system.time(
hd_sims <- map2_df(combos$key_id_1, 
                   combos$key_id_2, 
                   get_hd_distance, 
                   long_data))

# fast python hausdorff - this is actually similar to MDH, but maybe with scale it's a lot better?
py2 <- reticulate::py_run_file("../R_scripts/hausdorff_fast_wrapper.py")
system.time(
hd_sims <- map2_df(combos$key_id_1, 
                   combos$key_id_2, 
                   get_hd_distance_fast, 
                   long_data,
                   py2)
)
```

Hausdorff Distance Points only
```{r}
point_data <- raw_data %>%
  filter(key_id %in% img_nums) %>%
  mutate(key_id_name = key_id) %>%
  rename(x_line = x, y_line = y)

system.time(
pts <- map2_df(combos$key_id_1, 
                   combos$key_id_2, 
                   get_hd_distance_fast, 
                   point_data,
                   py2)
)
 
 # They're very correlated 
 pts %>%
    rename(hd_sim_pt = hd_sim) %>%
    left_join(hd_sims) %>%
    do(tidy(cor.test(.$hd_sim, .$hd_sim_pt)))
```

Modified Hausdorff Distance
```{r}
# load python modfied haussdorff function
py <- reticulate::py_run_file("../R_scripts/mhausdorff.py")

system.time(
mhd_sims <- map2_df(combos$key_id_1, 
                   combos$key_id_2, 
                   get_mhd_distance, 
                   long_data,
                   py))
```


MHD Points only
```{r}
system.time(
pts <- map2_df(combos$key_id_1, 
                   combos$key_id_2, 
                   get_mhd_distance, 
                   point_data,
                   py2)
)

# They're very correlated 
pts %>%
  rename(mhd_sim_pt = mhd_sim) %>%
  left_join(mhd_sims) %>%
  do(tidy(cor.test(.$mhd_sim, .$mhd_sim_pt)))
```

Plot sims
```{r}
sims <- left_join(hd_sims, nn_sims) %>% 
  left_join(mhd_sims) %>%
  mutate(key_id_1 = as.factor(key_id_1),
         key_id_2 = as.factor(key_id_2))

sims$key_id_1 <- fct_recode(sims$key_id_1, 
                          tree_outline_1 = "6613114395033600",
                          tree_outline_2 = "6557761544388608",
                          tree_bushy_1 = "4736045847412736",
                          tree_xmas = "4688802348007424",
                          tree_bushy_2 = "5366456621465600",
                          tree_bushy_3 = "4707338638327808",
                          tree_outline_3 = "4653335464378368",
                          tree_bushy_4 = "5142905146572800")

sims$key_id_2 <- fct_recode(sims$key_id_2, 
                          tree_outline_1 = "6613114395033600",
                          tree_outline_2 = "6557761544388608",
                          tree_bushy_1 = "4736045847412736",
                          tree_xmas = "4688802348007424",
                          tree_bushy_2 = "5366456621465600",
                          tree_bushy_3 = "4707338638327808",
                          tree_outline_3 = "4653335464378368",
                          tree_bushy_4 = "5142905146572800")

sims$key_id_1 <- fct_relevel(sims$key_id_1, 
                             c("tree_outline_1",
                             "tree_outline_2",
                             "tree_outline_3",
                             "tree_bushy_1", 
                             "tree_bushy_2",
                             "tree_bushy_3",
                             "tree_bushy_4",
                             "tree_xmas"))


sims$key_id_2 <- fct_relevel(sims$key_id_2,
                             c("tree_outline_1",
                             "tree_outline_2",
                             "tree_outline_3",
                             "tree_bushy_1", 
                             "tree_bushy_2",
                             "tree_bushy_3",
                             "tree_bushy_4",
                             "tree_xmas"))
                        
ggplot(sims, aes(x = key_id_1, y = key_id_2, fill = cosine)) +
  geom_tile() +
  theme_bw()

sims %>%
 # filter(cosine > .997) %>%
  ggplot(aes(x = key_id_1, y = key_id_2, fill = cosine)) +
  geom_tile() +
  theme_bw()
```