---
title: Check stimuli for concept viz 1
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: true
    code_folding: hide
---
  
******
******
  
```{r setup, include = F}
rm(list=ls())

reticulate::use_python("/usr/local/bin/python") ## load this first otherwise get import errors

# load packages
library(knitr)
library(rmarkdown)
library(langcog)
library(tidyverse)
library(purrr)
library(feather)
library(forcats)
library(magick)
library(data.table)

source("../R_scripts/helpers.R")

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F, cache = T, fig.height = 4)
```

```{r}
ITEM <- "bread"
GDRAW_SIZE <- 255
IMAGENET_SIZE <- 224
N_INTERPOLATE <- 500 
N_ILE <- 10
```

## Check items befor running

Basic checks
```{r}
final_stimuli <- read_csv(paste0("../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/balanced_lists/", ITEM ,"_id_pairs_balanced_hd.csv"), col_types = list(col_character(), col_character(), col_double(), col_double(), col_character(), col_character())) %>%
  rename(hd_sim = hausdorff_sim)

## merge in nn data
these_nns <- read_feather(paste0("../../data/keras_similarities/pairwise_country/", ITEM , "_all_sims.txt")) %>%
  select(key_id_1, key_id_2, cosine) 

final_stim <- final_stimuli %>%
                left_join(these_nns) 

count(final_stim, haus_bin)
cor.test(final_stim$cosine, final_stim$hd_sim)
```


Confirm that pairs are sensible
```{r}
SIM_BIN <- 9

plot_ids <- final_stim %>%
  filter(haus_bin == SIM_BIN) %>%
  mutate(id = 1:n()) %>%
  sample_n(8) %>%
  gather(key_id_name, key_id_num, c(-3:-9)) %>%
  arrange(haus_bin) %>%
  mutate(key_id_num = as.factor(key_id_num)) %>%
  arrange(id)

long_files = paste0("../../data/hausdorff_similarities/pair_sim_drawings/images/drawings/", plot_ids$key_id_num, ".jpeg")

rl = lapply(long_files, image_read)
gl = lapply(rl, grid::rasterGrob)
gridExtra::grid.arrange(grobs = gl, nrow = 8)

```

## Save all measure in single csv
# Get Modified Hausdorff Distance for comparision
```{r}

final_stimuli <- read_csv(paste0("../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/balanced/lists", ITEM,"_id_pairs_balanced_hd.csv"),col_types = list(col_character(), col_character(), col_double(), col_double(), col_character(), col_character())) %>%
  rename(hd_sim = hausdorff_sim )

raw_data <- read_feather(paste0("../../data/raw_data/feathers/atleast_100/", ITEM, ".txt"))

### Get long data
unique_ids_in_pairs <- unique(c(final_stimuli$key_id_1, final_stimuli$key_id_2))
nested_raw <- raw_data %>%
  filter(key_id %in% unique_ids_in_pairs) %>%
  mutate(key_id_name = key_id) %>%
  group_by(key_id_name) %>%
  nest() 

long_data <- map_df(nested_raw$data, get_image_from_google_draw, 
                                      GDRAW_SIZE,
                                      IMAGENET_SIZE,
                                      N_INTERPOLATE, 
                                      return = "long") %>%
  #bind_rows() %>%
  mutate(key_id = as.factor(key_id))

py <- reticulate::py_run_file("../R_scripts/mhausdorff.py")

this_path <- paste0("../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/balanced_lists/", ITEM, "_balanced_sims_mhd.csv")

mhd_sims <- map2_df(final_stimuli$key_id_1, 
                    final_stimuli$key_id_2, 
                    get_mhd_distance, 
                    long_data,
                    py,
                    write = TRUE,
                    path = this_path)
```


Merge all measures together and write to csv (mhd, hd, cosine)
```{r}

mhd <- read_csv(paste0("../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/balanced_lists/", ITEM, "_balanced_sims_mhd.csv"), col_names = FALSE, col_types = list(col_character(), col_character(), col_double())) %>%
  rename(key_id_1 = X1,
         key_id_2 = X2,
         mhd_sim = X3)

all_measures <- final_stim %>%
  left_join(mhd)

write_csv(all_measures, paste0("../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/balanced_lists/", ITEM, "_all_measures.csv"))





