---
title: Summary of drawing analyses
subtitle: 
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: false
    theme: cerulean
    toc_float: false
    toc: true
    code_folding: hide
---
  
******
******

```{r setup, include = F}
rm(list=ls())

# load packages
library(tidyverse) 
library(knitr)
library(rmarkdown)
library(purrr)
library(broom)
library(langcog)
library(magrittr)
library(rworldmap)
library(ggjoy)
library(feather)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F,  cache = F, fig.height = 4)

mapTheme = theme(plot.background = element_blank(),
                 panel.grid.major = element_blank(),
                 panel.grid.minor = element_blank(),
                 panel.border = element_blank(),
                 panel.background = element_blank())
```  

The [Quick Draw](https://quickdraw.withgoogle.com/) Dataset is a collection of [50 million drawings across 345 categories](https://github.com/googlecreativelab/quickdraw-dataset). Using the Brysbaert concretneess norms (Brysbaert, Warriner, & Kuperman, 2013), I selected the subset of drawing cues that were in the top and bottom 6-tile of concreteness (n = 109). I then download the "simplified" datasets for this set of cues from: https://console.cloud.google.com/storage/browser/quickdraw_dataset/full/simplified. The drawings have been pre-scaled so they are all 255 x 255. The simplified versions also do not have time information. I then munged jsons to be in long form and saved them as a  feather file (munge_jsons.R).

## Sanity check
This is what the drawings look like:
(random sampling of 30 drawings for 1 cue)
```{r, fig.height = 6}
ITEM <- "tree"
N_DRAWINGS <- 30

ex <- read_feather(paste0("../../data/raw_data/feathers/atleast_1500/", ITEM, ".txt"))

ex %>%
  filter(key_id %in% sample(unique(ex$key_id), N_DRAWINGS)) %>% # sample N
  ggplot(aes(x = x, y = -y, color = country, alpha = recognized)) +
  ggtitle(ITEM)+
  facet_wrap(~key_id) +
  geom_point() +
  geom_path(aes(group = stroke_num)) +
  theme_bw()
```


## Summary stats

```{r}
# Read in summary drawing data
d <- list.files("../../data/summary_data/") %>%
  purrr::map(function(x) paste0("../../data/summary_data/", x)) %>% 
  purrr::map(read_feather) %>% 
  bind_rows() 
```

### Number of participants per country
```{r}
d %>% 
  group_by(country) %>%
  summarize(`total drawings` = sum(n)) %>%
  arrange(-`total drawings`) %>%
  kable()
```

### Number of cues per country

The missing items are because we only include an item for a country if there were at least 1500 participants.
```{r}
MIN_NUM_ITEMS <- 40

item_counts = d %>%
  ungroup() %>%
  count(country) %>%
  arrange(-`nn`)
  
kable(item_counts)

big.countries <- item_counts %>%
                    filter(nn > MIN_NUM_ITEMS)

d %<>% filter(country %in% big.countries$country)
```

The analyses below only include countries with at least `r MIN_NUM_ITEMS` items.


### Number of participants per cue

```{r}
d %>% 
  group_by(word) %>%
  summarize(`total drawings` = sum(n)) %>%
  arrange(-`total drawings`) %>%
  kable()
```


## By-country summaries
Below is the distribution over __items__ within each country for a number of different measures. The measures are: stroke length, number of strokes, proportion recognized by google. 

### Stroke length{.tabset}

#### Joy plot
```{r, fig.height = 7}
ggplot(d, aes(x = mean_lengths, y = reorder(country, mean_lengths))) + 
  geom_joy(scale = 2, aes(color = country), alpha = .3, size = 1) +
  theme_joy(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        legend.position = "none")
```

#### Map
```{r}
geo_codes <- read_csv("../../data/supplementary_data/geo_codes.csv")

d %<>% left_join(geo_codes, by = c("country" = "countries"))

d %>%
  group_by(country, lat, lon) %>%
  summarize(mean_lengths = mean(mean_lengths)) %>%
  ggplot() +     
  borders("world", colour="gray50", fill="gray50") +
  geom_point(aes(x = lon, y=lat, 
                 color = mean_lengths),size = 3) +
  scale_color_gradient2(midpoint = median(d$mean_lengths, na.rm = T), 
                          low = "green", mid = "white", high = "red") +
  mapTheme
```

### Num Strokes{.tabset}

#### Joy plot
```{r, fig.height = 7}
ggplot(d, aes(x = mean_n_strokes, y = reorder(country, mean_n_strokes))) + 
  geom_joy(scale = 3, aes(color = country), alpha = .3, size = 1) +
  theme_joy(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        legend.position = "none")
```

#### Map
```{r}
d %>%
  group_by(country, lat, lon) %>%
  summarize(mean_n_strokes = mean(mean_n_strokes)) %>%
  ggplot() +   
  borders("world", colour="gray50", fill="gray50") +
  geom_point(aes(x = lon, y=lat, 
                 color = mean_n_strokes),size = 3) +
    scale_color_gradient2(midpoint = median(d$mean_n_strokes, na.rm = T), 
                          low = "green", mid = "white", high = "red") +
  mapTheme
```

### Prop recognized{.tabset}

#### Joy plot
```{r, fig.height = 7}
ggplot(d, aes(x = prop_recognized, y = reorder(country, prop_recognized))) + 
  geom_joy(scale = 3, aes(color = country), alpha = .3, size = 1) +
  theme_joy(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        legend.position = "none")
```

#### Map
```{r}
d %>%
  group_by(country, lat, lon) %>%
  summarize(prop_recognized = mean(prop_recognized)) %>%
  ggplot() +   
  borders("world", colour="gray50", fill="gray50") +
  geom_point(aes(x = lon, y=lat,
                 color = prop_recognized),size = 3) +
    scale_color_gradient2(midpoint = median(d$prop_recognized, na.rm = T), 
                          low = "green", mid = "white", high = "red") +
  mapTheme
```

## By-item summaries
Below is the distribution over __countries__  for each item for a number of different measures. The measures are: stroke length, number of strokes, and proportion recognized by google. 


### Stroke length{.tabset}
```{r, fig.height = 30}
ggplot(d, aes(x = mean_lengths, y = reorder(word, mean_lengths))) + 
  geom_joy(scale = 3, aes(color = word), alpha = .3, size = 1) +
  theme_joy(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        legend.position = "none")
```

### Num Strokes{.tabset}
```{r, fig.height = 30}
ggplot(d, aes(x = mean_n_strokes, y = reorder(word, mean_n_strokes))) + 
  geom_joy(scale = 3, aes(color = word), alpha = .3, size = 1) +
  theme_joy(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        legend.position = "none")
```

### Prop recognized{.tabset}
```{r, fig.height = 30}
ggplot(d, aes(x = prop_recognized, y = reorder(word, prop_recognized))) + 
  geom_joy(scale = 3, aes(color = word), alpha = .3, size = 1) +
  theme_joy(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        legend.position = "none")
```
