---
title: Predicting variability in summary statistics
subtitle: 
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: false
    theme: cerulean
    toc_float: false
    toc: true
    code_folding: hide
---
  
******
******

```{r setup, include = F}
rm(list=ls())

# load packages
library(tidyverse) 
library(knitr)
library(rmarkdown)
library(purrr)
library(broom)
library(langcog)
library(magrittr)
library(feather)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F,  cache = F, fig.height = 4)

mapTheme = theme(plot.background = element_blank(),
                 panel.grid.major = element_blank(),
                 panel.grid.minor = element_blank(),
                 panel.border = element_blank(),
                 panel.background = element_blank())
```  


```{r}
#Read in drawing summary data

d <- list.files("../../data/summary_data/") %>%
  map(function(x) paste0("../../data/summary_data/", x)) %>% 
  map(read_feather) %>% 
  bind_rows() 
```

Item and countries vary along a number of measures. Can we predict this variablity?

=> the only predictors included here are 1st language status (for countries) and  concretness (for items). There are infinitely other possible predictors. Which would be theoretically interesting?

## Country variability
### first language status
```{r}
english_countries <- c("Australia", 
                      "Canada",
                      "United Kingdom", 
                      "United States")

d %<>% 
  mutate(lang = ifelse(country %in% english_countries, "english", "non_english"))
```

```{r}
d %>%
  gather(measure, value, c(4:8)) %>%
  ggplot(aes(y = value, x= lang, fill = lang)) +
    facet_wrap(~measure, scales = "free") +
    geom_boxplot() +
    theme_bw() +
    theme(legend.position = "none")
```

No difference here

## Item variability

### concreteness
```{r}
cues <- read_csv("../../data/supplementary_data/extreme_cues.csv") %>%
  select(cue, conc.bin)

d %<>% left_join(cues, by=c("word" = "cue")) %>%
  mutate(conc.bin = as.factor(conc.bin))

d %>%
  filter(!is.na(conc.bin)) %>%
  gather(measure, value, c(4:8)) %>%
  ggplot(aes(y = value, x= conc.bin, fill = conc.bin)) +
    facet_wrap(~measure, scales = "free") +
    geom_boxplot() +
    theme_bw() +
    theme(legend.position = "none")
```

### concretness and first language status
```{r, fig.height = 3}
summaries <- d %>%
  filter(!is.na(conc.bin)) %>%
  gather(measure, value, c(4,6, 8)) %>% 
  filter(!is.na(value))  %>%
  group_by(measure, conc.bin, lang) %>%
  multi_boot_standard(column = "value", na.rm = TRUE)

ggplot(summaries, aes(x = lang, y = mean,
                      fill = conc.bin, color = conc.bin, group = conc.bin)) +
    facet_wrap(~measure, scales = "free") +
    geom_pointrange(aes(ymax = summary_ci_upper, ymin = summary_ci_lower), 
                   position=position_dodge(.9), size = .4) +
    theme_bw() 
```

Abstract words have longer strokes for both English and non-English speakers. Also, difference in accuracy between low and high concreteness words larger for non-english speakers.
