---
title: Explore pairwise country similarities for drawings
subtitle: 
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: true
---
  
******
******
  
```{r setup, include = F}
rm(list=ls())

# load packages
library(knitr)
library(rmarkdown)
library(langcog)
library(tidyverse)
library(stringr)
library(purrr)
library(corrr)
library(countrycode)
library(ggjoy)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F, cache = F, fig.height = 4)
```
Here we're just looking at one item: __tree__

Read in drawing pairwise-sims file. 
```{r}
tree <- read_csv("../../data/keras_similarities/pairwise_country/tree_pairwise_sims.csv") %>%
    mutate(key_id_1 = as.character(key_id_1),
           key_id_2 = as.character(key_id_2))

```

Number of unique participants per each country (sampled 50). We take the 34 biggest countries. (Note that for even smaller countries, some duplicates)
```{r}
tree_big = tree %>%
  group_by(country_code_1, key_id_1)%>%
  slice(1) %>%
  ungroup() %>%
  count(country_code_1)%>%
  arrange(-n)%>%
  as.data.frame() %>%
  slice(1:34)

kable(tree_big)
```

Remove NAs- very few, but not sure where they come from. Need to look into this. Subset to only big countries.
```{r}
tree_clean <- tree %>%
  filter(!is.na(cosine)) %>%
  filter(country_code_1 %in% tree_big$country_code_1 & country_code_2 %in%   tree_big$country_code_1)
```

```{r}
get_unique_relation_id <- function (x, y){
  pairs = c(x, y)
  ordered = order(pairs)
  paste0(pairs[ordered[1]], pairs[ordered[2]])
}

tree_means <- tree_clean %>%
  group_by(country_code_1, country_code_2) %>%
  summarize(mean_cosine = mean(cosine),
            sd = sd(cosine),
            norm_mean = mean_cosine/sd) %>%
  rowwise() %>%
  mutate(all_codes = get_unique_relation_id(country_code_1, country_code_2)) %>%
  group_by(all_codes)%>%
  slice(1) %>%
  ungroup()%>%
  mutate(country_name_1 = as.factor(countrycode(country_code_1, "iso2c","country.name")),
         country_name_2 = as.factor(countrycode(country_code_2, "iso2c","country.name")),
         country_names = paste0(country_name_1,"_", country_name_2),
         continent_name_1 = as.factor(countrycode(country_code_1, 'iso2c', 'continent')),
         continent_name_2 = as.factor(countrycode(country_code_2, 'iso2c', 'continent')),
         cont_order_1 = unclass(continent_name_1) %>% as.numeric,
         cont_order_2 = unclass(continent_name_2) %>% as.numeric) %>%
  select(-country_code_1, -country_code_2, -continent_name_1, -continent_name_2) %>%
  arrange(-mean_cosine)
```


## Similarity distributions by country
Distribution of mean country-wise similarities: Looks to be correlation between mean and varaince. 
```{r, fig.height = 6}
tree_means %>%
  ungroup() %>%
  select(mean_cosine, country_name_1, country_name_2) %>%
  gather("country", "country_name", 2:3) %>%
  select(-country) %>%
  ggplot(aes(x = mean_cosine, y = reorder(country_name, mean_cosine))) + 
  geom_joy(scale = 2, aes(color = country_name), alpha = .3, size = 1) +
  theme_joy(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        legend.position = "none")

tree_means %>%
  ungroup() %>%
  select(mean_cosine, sd, country_name_1, country_name_2) %>%
  gather("country", "country_name", 3:4) %>%
  select(-country) %>%
  ggplot(aes(x = mean_cosine, y = reorder(country_name, sd))) + 
  geom_joy(scale = 2, aes(color = country_name), alpha = .3, size = 1) +
  theme_joy(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        legend.position = "none")

tree_means %>%
  ungroup() %>%
  select( norm_mean, country_name_1, country_name_2) %>%
  gather("country", "country_name", 2:3) %>%
  select(-country) %>%
  ggplot(aes(x = norm_mean, y = reorder(country_name, norm_mean))) + 
  geom_joy(scale = 2, aes(color = country_name), alpha = .3, size = 1) +
  theme_joy(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        legend.position = "none")
```

Pairwise similarity:
```{r, fig.height = 6}
tree_means_2 = tree_means %>%
  mutate(country_name_3 = country_name_1,
         country_name_1 = country_name_2, 
         country_name_2 = country_name_3,
         cont_order_3 = cont_order_1,
         cont_order_1 = cont_order_2, 
         cont_order_2 = cont_order_3) %>%
  select(-country_name_3, -cont_order_3)    

all = tree_means %>%
    bind_rows(tree_means_2) %>%
    mutate(country_name_1 = fct_reorder(country_name_1, cont_order_1), 
           country_name_2 = fct_reorder(country_name_2, cont_order_2)) 
  
all %>%
  ggplot(aes(x = country_name_1, 
             y = country_name_2)) +
  geom_raster(aes(fill = norm_mean)) + 
  scale_fill_continuous(low = "#ffffcc", high = "#800026") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1, vjust = 1, size = 6),
        axis.text.y = element_text(size = 6),
        axis.title = element_blank())

```

Within country similarity is not necessarily bigger than across country. Note that when within country similarity is low, all across country variability also low.


## Dyadic predictive measures

Centroid geographic distance and linguistic distance. 
Continuous linguistic measures come from here: https://github.com/ddediu/lgfam-newick/blob/master/paper/family-trees-with-brlength.pdf. 
```{r}
dyadic <- read_csv("../../data/supplementary_data/cultural_sim_measures/all_dyadic_vars.csv") 
#dyadic2 <- dyadic %>%
#  rowwise() %>%
#  mutate(all_codes = get_unique_relation_id(country_code_1, country_code_2)) %>%
#  select(-country_code_1, -country_code_2) %>%
#  ungroup()
# write_csv(dyadic2, "../../data/supplementary_data/cultural_sim_measures/all_dyadic_vars2.csv")
dyadic2 <- read_csv("../../data/supplementary_data/cultural_sim_measures/all_dyadic_vars2.csv") %>%
  select(all_codes, everything()) 

is.na(dyadic2) <- do.call(cbind,lapply(dyadic2, is.infinite))
dyadic_clean <- dyadic2 %>%
  mutate(all_codes = as.factor(all_codes)) %>%
  group_by(all_codes) %>%
  summarize(wals_euclidean_dist = mean(wals_euclidean_dist, na.rm = TRUE),
            asjp_dist = mean(asjp_dist, na.rm = TRUE),
            centroid_dist_meters = mean(centroid_dist_meters, na.rm = TRUE))
```

Summary of dyadic measures:
```{r, fig.height = 3}
summary(dyadic_clean)

dyadic_clean %>%
  gather("measure", "value" , 2:4)  %>%
  ggplot(aes(x = value, fill = measure)) +
  geom_histogram() +
  facet_wrap(~measure, scales = "free") +
  theme_bw() +
  theme(legend.position = "none")
```

Correlations:
```{r}
correlate(dyadic_clean %>% select(-1),
                   use = "complete.obs")  %>%
  shave() %>%
  kable()
```


## Dyadic measures predicting pairwise country variance in simiarities{.tabset}

### Distance
```{r, fig.height = 6}
all <- left_join(tree_means, dyadic_clean)

all_2 = all %>%
  mutate(country_name_3 = country_name_1,
                   country_name_1 = country_name_2, 
                   country_name_2 = country_name_3) %>%
  select(-country_name_3) 


all %>%
  bind_rows(all_2)%>%
  filter(country_name_1 != country_name_2) %>%
  ggplot(aes(x = country_name_1,
             y = country_name_2)) +
  geom_raster(aes(fill = centroid_dist_meters)) +
  scale_fill_gradientn(colours = terrain.colors(10)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, vjust =.25, size = 4),
        axis.text.y = element_text(size = 4),
        axis.title = element_blank()) 
```

```{r, fig.height = 6}
all %>%
  filter(country_name_1 != country_name_2) %>%
  ggplot(aes(x = centroid_dist_meters, y = mean_cosine)) +
  geom_label(aes(label = all_codes)) +
  geom_smooth(method = "lm")
```

### ASJP language distance

```{r, fig.height = 6}
all %>%
  bind_rows(all_2)%>%
  filter(country_name_1 != country_name_2) %>%
  ggplot(aes(x = country_name_1,
             y = country_name_2)) +
  geom_raster(aes(fill = asjp_dist)) +
  scale_fill_gradientn(colours = terrain.colors(10)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, vjust =.25, size = 4),
        axis.text.y = element_text(size = 4),
        axis.title = element_blank()) 
```

```{r, fig.height = 6}
all %>%
  filter(country_name_1 != country_name_2) %>%
  ggplot(aes(x = asjp_dist, y = mean_cosine)) +
  geom_label(aes(label = all_codes)) +
  geom_smooth(method = "lm")
```


### WALS language distance
```{r, fig.height = 6}
all %>%
  bind_rows(all_2)%>%
  filter(country_name_1 != country_name_2) %>%
  ggplot(aes(x = country_name_1,
             y = country_name_2)) +
  geom_raster(aes(fill = wals_euclidean_dist)) +
  scale_fill_gradientn(colours = terrain.colors(10)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, vjust =.25, size = 4),
        axis.text.y = element_text(size = 4),
        axis.title = element_blank()) 
```

```{r, fig.height = 6}
all %>%
  filter(country_name_1 != country_name_2) %>%
  ggplot(aes(x = wals_euclidean_dist, y = mean_cosine)) +
  geom_label(aes(label = all_codes)) +
  geom_smooth(method = "lm")
```

```{r, eval = F, include = F}
us_trees = tree_clean %>%
  filter(country_code_1 == "BR" & country_code_2 == "MA") %>%
  arrange(cosine) 

dyadic_clean = dyadic %>%
  group_by(all_codes)  %>%
  summarize(normalized_n_events_all = mean(normalized_n_events_all, na.rm = FALSE),
            normalized_mean_imports_dollars = mean(normalized_mean_imports_dollars, na.rm = FALSE),
            wals_euclidean_dist = mean(wals_euclidean_dist, na.rm = FALSE),
            asjp_dist = mean(asjp_dist, na.rm = FALSE),
            centroid_dist_meters = mean(centroid_dist_meters, na.rm = FALSE))
```

```{r}
all_complete = all %>%
        filter(!is.na(wals_euclidean_dist) & !is.na(centroid_dist_meters)) %>%
    
m = summary(lm(mean_cosine~ wals_euclidean_dist +  centroid_dist_meters, all_complete))

summary(lm(mean_cosine~ centroid_dist_meters, all_complete))



``