---
title: Predict pairwise similarities
subtitle: 
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: false
    code_folding: hide
---
  
******
******
  
```{r setup, include = F}
rm(list=ls())

# load packages
library(knitr)
library(rmarkdown)
library(langcog)
library(tidyverse)
library(stringr)
library(corrr)
library(countrycode)
library(forcats)
library(broom)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F, cache = F, fig.height = 4)
```

```{r}
ITEM <- "bread"
``` 
Here we're just looking at one item: __`r ITEM`__

```{r}
get_unique_relation_id <- function (x, y){
  pairs = c(x, y)
  ordered = order(pairs)
  paste0(pairs[ordered[1]], pairs[ordered[2]])
}

ratios <- read_csv(paste0("../../data/keras_similarities/pairwise_country/",ITEM, "_sim_ratios.csv")) %>%
  rowwise() %>%
  mutate(all_codes = get_unique_relation_id(country_code_1, country_code_2))  %>%
  ungroup() %>%
  select(all_codes, everything()) %>%
  mutate(country_name_1 = as.factor(country_name_1),
         country_name_2 = as.factor(country_name_2))

```

## Dyadic predictive measures

Centroid geographic distance and linguistic distance. 
Continuous linguistic measures come from here: https://github.com/ddediu/lgfam-newick/blob/master/paper/family-trees-with-brlength.pdf. 
```{r}
dyadic <- read_csv("../../data/supplementary_data/cultural_sim_measures/all_dyadic_vars.csv") %>%
  rowwise() %>%
  mutate(all_codes = get_unique_relation_id(country_code_1, country_code_2)) %>%
  ungroup() %>%
  select(-country_code_1, -country_code_2) 

is.na(dyadic) <- do.call(cbind,lapply(dyadic, is.infinite))

dyadic_clean <- dyadic %>%
  mutate(all_codes = as.factor(all_codes)) %>%
  group_by(all_codes) %>%
  slice(1) %>%
  select(all_codes, everything()) %>%
  ungroup()
```

Merge together dists and sims

Note there a bunch of different ratios we could use here since it's not symmetrical. Here I'm taking the average of the two.
```{r, eval = F}
all0 <- ratios %>%
  left_join(dyadic_clean, by = "all_codes") %>%
  select(all_codes, everything())

all1 <- ratios %>%
  group_by(all_codes) %>%
  slice(1) %>%
  left_join(dyadic_clean, by = "all_codes") %>%
  select(all_codes, everything())%>%
  mutate(country_name_1 = as.factor(country_name_1),
         country_name_2 = as.factor(country_name_2))

all2 <- ratios %>%
  group_by(all_codes) %>%
  slice(2) %>%
  left_join(dyadic_clean, by = "all_codes") %>%
  select(all_codes, everything())%>%
  mutate(country_name_1 = as.factor(country_name_1),
         country_name_2 = as.factor(country_name_2))
```

```{r}
all <- ratios %>%
  #mutate(all_codes = as.factor(all_codes)) %>%
  group_by(all_codes) %>%
  summarize(mean_ratio = mean(mean_ratio)) %>%
  ungroup()%>%
  left_join(dyadic_clean %>% mutate(all_codes = as.character(all_codes)), by = "all_codes")  %>%
  ungroup() %>%
  select(all_codes, everything())  %>%
  separate(all_codes, c("country_code_1", "country_code_2"), sep = 2, remove = F)  %>%

  left_join(ratios %>% select(country_code_1, cont_order_1) %>% distinct()) %>%
  left_join(ratios %>% select(country_code_2, cont_order_2) %>% distinct()) %>%
  left_join(ratios %>% select(country_code_1, country_name_1) %>% distinct()) %>%
  left_join(ratios %>% select(country_code_2, country_name_2) %>% distinct()) %>%
  mutate(country_name_1 = as.factor(country_name_1),
         country_name_2 = as.factor(country_name_2)) 
```

### Distance

```{r, fig.height = 6}
all %>%
  filter(country_name_1 != country_name_2) %>%
  ggplot(aes(x = centroid_dist_meters, y = mean_ratio)) +
  geom_point() +
  #geom_label(aes(label = all_codes)) +
  geom_smooth(method = "lm") +
  theme_minimal()
```

### ASJP language distance


```{r, fig.height = 6}
all %>%
  #filter(asjp_dist > 0) %>%
  filter(country_name_1 != country_name_2) %>%
  ggplot(aes(x = asjp_dist, y = mean_ratio)) +
  #geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal()
```

### WALS language distance

```{r, fig.height = 6}
all %>%
  #filter(wals_euclidean_dist > 0) %>%
  filter(country_name_1 != country_name_2) %>%
  ggplot(aes(x = wals_euclidean_dist, y = mean_ratio)) +
  #geom_point() +
  #geom_label(aes(label = all_codes)) +
  geom_smooth(method = "lm") +
  theme_minimal()
```

```{r}
lm(mean_ratio ~ centroid_dist_meters , all) %>%
  tidy () %>%
  kable()

lm(mean_ratio ~ asjp_dist, all) %>%
  tidy () %>%
  kable()

lm(mean_ratio ~ wals_euclidean_dist , all) %>%
    tidy () %>%
  kable()

lm(mean_ratio ~ asjp_dist + centroid_dist_meters, all) %>%
  tidy () %>%
  kable()

lm(mean_ratio ~ wals_euclidean_dist + centroid_dist_meters, all) %>%
  tidy () %>%
  kable()
```
